---
title: "Buzzmetrics"
author: "Team Buzzmetrics"
date: "24 September 2014"
output: html_document
---

Packages:

install.packages('data.table')
install.packages('ggplot2')

Some preliminaries...

```{r}
require(data.table)
require(ggplot2)
require(reshape)

dataPath <- '../data'
```

Helper to read a CSV file in the data path keyed by DOI:

```{r}
readDataFileWithDOI <- function(fileName) {
  table <- data.table(read.csv(file.path(dataPath, fileName), header=TRUE))
  setkey(table, 'doi')
  table
}
```

Load data from the various feature files:

```{r}
dataStem <- file.path('altmetric','1d-2014-09-24')
#dataStem <- file.path('altmetric','1m-partial-2014-09-24')
outFilePath <- function(fileName) { file.path('out', dataStem, fileName) }

titles <- readDataFileWithDOI(paste0(dataStem, '.csv'))

questionMarks <- readDataFileWithDOI(outFilePath('question_marks.csv'))
questionMarks$question_marks <- factor(questionMarks$question_marks)

colons <- readDataFileWithDOI(outFilePath('colons.csv'))
colons$colons <- factor(colons$colons)

titleLengths <- readDataFileWithDOI(outFilePath('title_lengths.csv'))
titleLengths <- data.table(doi = titleLengths$doi,
                           title_length = titleLengths$length)

wordPrevalence <- readDataFileWithDOI(outFilePath('word_prevalence.csv'))

averageWordLength <- readDataFileWithDOI(outFilePath('average_word_length.csv'))
medianWordLength <- readDataFileWithDOI(outFilePath('median_word_length.csv'))

hasInitialism <- readDataFileWithDOI(outFilePath('has_initialism.csv'))
hasInitialism$has_initialism <- factor(hasInitialism$has_initialism)

adjective <- readDataFileWithDOI(outFilePath('adjective.csv'))
adjective <- adjective[,c('doi','adjective_count','total_words'),with=FALSE]
adverb <- readDataFileWithDOI(outFilePath('adverb.csv'))
adverb <- adverb[,c('doi','adverb_count'),with=FALSE]
noun <- readDataFileWithDOI(outFilePath('noun.csv'))
noun <- noun[,c('doi','noun_count'),with=FALSE]
preposition <- readDataFileWithDOI(outFilePath('preposition.csv'))
preposition <- preposition[,c('doi','preposition_count'),with=FALSE]
pronoun <- readDataFileWithDOI(outFilePath('pronoun.csv'))
pronoun <- pronoun[,c('doi','pronoun_count'),with=FALSE]
verb <- readDataFileWithDOI(outFilePath('verb.csv'))
verb <- verb[,c('doi','verb_count'),with=FALSE]
```

Go from publication date to an age in weeks, which is a bit easier to interpret:

```{r}
titles$pub_date <- as.POSIXct(titles$pub_date)
titles$age_weeks <- as.numeric(difftime(as.POSIXct('2014-09-25', tz='UTC'),
                                        titles$pub_date,
                                        units="weeks"))
```

Merge everything together on DOI:

```{r}
data <- titles
data <- data[questionMarks]
data <- data[colons]
data <- data[titleLengths]
data <- data[wordPrevalence]
data <- data[averageWordLength]
data <- data[medianWordLength]
data <- data[hasInitialism]
data <- data[adjective]
data <- data[adverb]
data <- data[noun]
data <- data[preposition]
data <- data[pronoun]
data <- data[verb]
```

Summary table:

```{r}
print(summary(data))
```

Some simple plots (none very helpful):

```{r, echo=FALSE}
#meltedData <- melt(data[,c('doi', 'age_weeks', 'score', 'question_marks',
#                           'colons'), with=FALSE],
#                   id=c('doi', 'age_weeks', 'score'))
#ggplot(meltedData) + geom_point(aes(x=age_weeks, y=log(score))) + facet_grid(variable ~ value)
```

```{r, echo=FALSE}
#ggplot(data) + geom_point(aes(x=age_weeks, y=log(score), color=title_length))
```

```{r, echo=FALSE}
#ggplot(data) + geom_point(aes(x=age_weeks, y=log(score), color=word_prevalence_score))
```

# Regressions

## Additive with Title Length

The simplest regression that could possibly work:

```{r}
lm1 <- lm(score ~ age_weeks + question_marks + colons + title_length,
          data=data)
print(summary(lm1))
```

The $R^2$ is very low. Let's have a look at $\log(score)$ to see if it fits better.

```{r}
lm2 <- lm(log(score) ~ age_weeks + question_marks + colons + title_length,
          data=data)
print(summary(lm2))
print(exp(lm2$coefficients))
```

It does indeed fit a bit better ($R^2$ is higher).

## The Kitchen Sink

```{r}
bigLm <- lm(score ~ age_weeks + question_marks + colons + title_length +
              word_prevalence_score + adjective_count + adverb_count +
              noun_count + preposition_count + pronoun_count + total_words +
              average_word_length + median_word_length + has_initialism,
            data=data)
print(summary(bigLm))
```

```{r}
bigLm <- lm(log(score) ~ age_weeks + question_marks + colons + title_length +
              word_prevalence_score + adjective_count + adverb_count +
              noun_count + preposition_count + pronoun_count + total_words +
              average_word_length + median_word_length + has_initialism,
            data=data)
print(summary(bigLm))
print(exp(bigLm$coefficients))
```

## Word types

```{r}
bigLm <- lm(log(score) ~ age_weeks + question_marks + colons +
              word_prevalence_score + adjective_count + adverb_count +
              noun_count + preposition_count + pronoun_count + total_words,
            data=data)
print(summary(bigLm))
print(exp(bigLm$coefficients))
```
